### 2023-10-20 results/celegans.tex
Going to lunch

@@

\begin{figure}[H]
  \centering
  \includesvg[width=\linewidth]{results/celegans/out5.svg}
  \caption{Analog predictions of the 5th data sequence.}
  \label{graph:celegansAnalog0}
\end{figure}

>>>>

Let's focus on a single data sequence, for simplicity. The training data sequence found in \cref{graph:io5Celegans}.

@@

\begin{figure}[H]
  \centering
  \includesvg[width=\linewidth]{results/celegans/out5}
  \caption{Analog predictions of the 5th data sequence.}
  \label{graph:celegansAnalog0}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{minipage}{\columnwidth}
    \subfloat[Training dataset sample\label{graph:io5Celegans}]{\includesvg[width=0.5\textwidth, pretex=\tiny]{datasets/celegans/ioTrain0}}%
    \hfill
    \subfloat[Test dataset sample]{\includesvg[width=0.5\textwidth,pretex=\tiny]{datasets/celegans/ioTest0}}%
  \end{minipage}
  \begin{minipage}{\columnwidth}
    \subfloat[Training dataset sample]{\includesvg[width=0.5\textwidth, pretex=\tiny]{datasets/celegans/ioTrain1.svg}}%
    \hfill
    \subfloat[Validation dataset sample]{\includesvg[width=0.5\textwidth,pretex=\tiny]{datasets/celegans/ioValid0}}%
  \end{minipage}
  \caption{\ac{C. elegans} dataset samples}
  \label{graph:celegans}
\end{figure}
